\section{Sources}
\begin{enumerate}
	\item Sorting out Sorting Video \label{sorting-out-sorting}
	\item Top JS libraries 
	(https://medium.com/javascript-scene/top-javascript-libraries-tech-to-learn-in-2018-c38028e028e6)
	\label{top-js-libraries}
	\item Vue website \label{vue-website}
	\item Vuex website \label{vuex-website}
	% Printed Sources
	\item \label{source-a} John Domingue, Erkki Sutinen. \textbf{Software Visualization}. \textit{Journal of Visual Languages and Computing}. 2002. 
	\item \label{source-b} Tobias Lauer. \textbf{Reevaluating and Refining the Engagement Taxonomy}. \textit{ITiCSE}. 2008. 
	\item \label{source-c} Christopher Hundhausen, Sarah Douglas. \textbf{Shifting from ``High Fidelity'' to ``Low Fidelity'' Algorithm Visualization Technology}. \textit{Conference on Human Factors in Computing Systems}. 2000. 
%	\item \label{source-d} Pilu Crescenzi. \textbf{Using AVs to Explain NP-completeness}. \textit{ITiCSE}. 2010. 
%	\item \label{source-e} Guido Rößling, Florian Lindner. \textbf{Visualizing Compression Algorithms on-the-fly}. \textit{ITiCSE}. 2009. 
	\item \label{source-f} Guido Rößling, Thomas L. Naps. \textbf{A Testbed for Pedagogical Requirements in Algorithm Visualization}. \textit{ITiCSE}. 2002. 
%	\item \label{source-g} David Burlinson et. al. \textbf{Bridges: A System to Enable Creation of Engaging Data Structures Assignments with Real-World Data and Visualizations}. \textit{SIGCSE}. 2016. 
	\item \label{source-h} Guido Rössling, Bernd Freisleben. \textbf{ANIMAL: A System for Supporting Multiple Roles in Algorithm Animation}. \textit{Journal of Visual Languages and Computing}. 2002. 
	\item \label{source-i} Steven Hansen, N. Hari Narayanan, Mary Hegarty. \textbf{Designing Educationally Effective Algorithm Visualizations}. \textit{Journal of Visual Languages and Computing}. 2002. 
	\item \label{source-j} Christopher Hundhausen, Sarah Douglas, John Stasko. \textbf{A Meta-Study of Algorithm Visualization Effectiveness}. \textit{Journal of Visual Languages and Computing}. 2002. 
\end{enumerate}