\hspace{-0.3in}
Algorithm Visualizations are most effective when they are interactive. 
AV's are more than just videos or animations that show the runtime process of an algorithm, 
where videos/animations are no more effective than traditional teaching methods 
AV's have been shown to improve student understanding of algorithms across. 
But even the most effective tools are useless if they don't get used. 
\newline\newline
I set out to create a lecture-enhancing AV tool 
to be used by Computer Science instructors teaching Algorithms.
The main objective being to create a tool that instructors will want to use. 
My target audience was the faculty at CSUN teaching algorithms. 
Having a background as a high school teacher, as well as taking multiple algorithms classes at CSUN,
I have some insight into the needs of a lecturer and also the student. 
\newline\newline
I based the design of this project around my experience in Comp 496ALG (now relabeled Comp 482),
covering three different algorithms taught in that class: \textsc{Stable Marriage}, \textsc{Interval
Scheduling}, and \textsc{Closest Pair of Points}. 
For each topic I created 
an \textsc{Instance Maker} interface to create and edit instances of the problem, 
a \textsc{Solver} to perform the algorithm step-by-step, 
and a \textsc{Display} to show a visual diagram.
\newline\newline
I demonstrated the product in front of two live classrooms, 
using the tool to enhance the lecture, engage the students, and pose some interesting questions. 
The feedback I received from these lectures was overly positive, both from the students and from the instructor. 